###Loading and preprocessing the data

We load the "activity.csv" data from the working directory and check the basic 
characteristics of the loaded dataset. We change the datatype of "date" column 
from factor data type to date datatype. 

```{r}
activity <- read.table("activity.csv",sep=",",quote="\"'",header=TRUE)
str(activity)
```

###What is mean total number of steps taken per day?

We need to create a histogram of the total number of steps taken each day. 
For this we will use ggplot2 R package as well as xtable, so please install them
before continuing.

```{r results='asis',echo=FALSE}
##install.packages("ggplot2")
##install.packages("xtable")
```

After installing ggplot2 R package proceed with creating the histogram.
```{r}
library(ggplot2)
stepperday <- aggregate(activity[,"steps"] ~ activity[,"date"],activity,sum)
names(stepperday) <- c("date","steps")
stepperday$date <- as.Date(stepperday$date,"%Y-%m-%d")
p <- ggplot(stepperday, aes(date, steps))
p <- p + geom_histogram(binwidth = 0.5, stat="identity", colour="white") 
p
```

A quick summary will tell us no. of steps mean and median for the whole dataset.
```{r}
summary(stepperday)
```

Here is the table of mean values for each day
```{r results='asis'}
stepperdaymean <- aggregate(activity[,"steps"] ~ activity[,"date"],
                            activity,
                            mean)
names(stepperdaymean) <- c("date","stepsmean")
library(xtable)

xt <- xtable(stepperdaymean)
print(xt, type="html")
```

Here is the table of median values for each day
```{r results='asis'}
stepperdaymedian <- aggregate(activity[,"steps"] ~ activity[,"date"],
                              activity,
                              median)
names(stepperdaymedian) <- c("date","stepsmedian")
xt <- xtable(stepperdaymedian)
print(xt, type="html")
```
